A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-15 paper/ms.tex
update ms

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler and TESS views of the $\delta$\,Lyr cluster.} Colored
    points are kinematically selected candidate $\delta$\,Lyr
    cluster members.  Both Kepler (gray panels) and TESS observed portions of
    the cluster.  Naked-eye stars ($m_{\rm V}<6.5$) are shown in gray or orange.
    Kepler\,1627 (green star) was observed during the entirety of the
    Kepler mission.  Colors of candidate cluster members indicate the
    duration of TESS observations to date.  So far, Kepler\,1627 has been
    observed by TESS for two lunar months.
    \label{fig:skychart}
	}
\end{figure}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f15c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is \clusterage\ old.}  {\it Top:}
    Color-absolute magnitude diagram of candidate \cn\ members, in addition to
    stars in IC\,2602 ($\approx38$\,Myr), the Pleiades ($\approx
    115$\,Myr; \citealt{dahm_2015}), and the Gaia EDR3 Catalog of
    Nearby Stars (gray background).  The zoomed right panel
    highlights the pre-main-sequence.  The \cn\ and IC\,2602 are
    approximately the same isochronal age.  {\it Bottom:} TESS and
    Kepler stellar rotation period versus dereddened Gaia color,
    with the Pleiades and Praesepe (650\,Myr) shown for reference
    \citep{rebull_rotation_2016a,douglas_poking_2017}.  Most
    candidate \cn\ members are gyrochronally younger than the
    Pleiades; outliers are probably field interlopers.
   \label{fig:age}
	}
\end{figure*}

@@

		\subfloat{
			\includegraphics[width=\textwidth]{f5.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The full Kepler dataset spans 1{,}437 days (3.9 years), sampled at
    30 minute cadence.  A one hundred day segment is shown here.  The
    top panel shows the \texttt{PDCSAP} median-subtracted flux in
    units of parts-per-thousand ($\times 10^{-3}$).  The dominant
    signal is induced by starspots.  The model for the stellar
    variability (orange line) is subtracted below, revealing the
    transits of \pn, as well as other deviations from the model.  The
    Figure Set online shows the entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627Ab, with stellar variability
    removed.  The 2-$\sigma$ model uncertainties and the maximum {\it
    a posteriori} model are shown as the faint purple band, and the
    dark purple line.  Gray points are individual \texttt{PDCSAP} flux
    measurements; black points are binned to 20 minutes, with a
    representative error bar shown.  The asymmetric residual visible
    during the transit is robust against detrending methods; we
    believe that it is caused by starspot crossings.
    \label{fig:lc}
  }
\end{figure*}

@@

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f16.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
    {\it Top:} 
    The time of each Kepler transit was measured, along with the local
    slope of the light curve.  The two quantities appear
    anti-correlated, which is most easily explained by starspot
    crossings during the first (second) half of transit inducing a
    positive (negative) TTV, provided that the orbit is prograde
    \citep{mazeh_time_2015}.  The units along the abscissa are most
    easily understood by considering that the stellar flux
    changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
    {\it Bottom:} Radial velocities acquired using Keck/HIRES during
    the transit of 2021 Aug 7, observed simultaneously with MuSCAT3
    ({\it griz} photometry).  A quadratic baseline trend was allowed
    in the RV fit.  The best-fit sky-projected obliquity in this model
    is listed in red; the detection however has marginal statistical
    significance compared to a ``trend-only'' model.
    \label{fig:obliquity}
	}
\end{figure}
\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f14.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting
			exoplanets}.  Planets older than $10^9$ years are shown with gray
		markers.  Planets younger than a gigayear with ${\rm
			\tau}/\sigma_{\rm \tau} > 3$ are emphasized, for $\tau$ the age.
		\pn\ is shown with a
		star.  The large sizes of the youngest transiting planets could be
		explained by their primordial atmospheres not yet having
		evaporated; direct measurements of the atmospheric outflows or
		planetary masses would help to confirm this expectation.
		Selection effects may also be important.  Parameters are from the
		NASA Exoplanet Archive (2021 July 2).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

Could the transit signal be produced by anything other than a planet
orbiting this near-solar analog?  \citet{morton_false_2016} validated
the planet based on the transit shape, arguing that the most probable 
false positive scenario was that of a background eclipsing binary,
which had a model-dependent probability of $\approx10^{-5}$.
As we describe in Appendix~\ref{app:companionstar} however,
Kepler\,1627A is accompanied by a low-mass stellar companion ($M_{\rm
B}\approx 0.44\,M_\odot$).  We therefore reconsidered this false
positive scenario in some detail.

@@

There are three new lines of evidence that support the planetary
interpretation.  First, the transit duration and the orbital period
are inconsistent with an eclipsing body around the M-dwarf companion:
we find $\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for the companion is
$\approx 3.2\,{\rm g\,cm}^{-3}$ (Table~\ref{tab:posterior};
\citealt{choi_mesa_2016}).  The transit duration is therefore too long
to be explained by a star eclipsing the M dwarf secondary at
$\approx$$5$-$\sigma$.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f17.pdf}
			\includegraphics[width=0.48\textwidth]{f6.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Kepler 1627 is a binary.} {\it Left:} High-resolution imaging
    from Gemini-North/`Alopeke and Keck/NIRC2 shows an $\approx$M2V
    companion at $\rho \approx 0\farcs16$, which corresponds to a
    projected separation of $53\pm4$\,AU.  The inset shows a cutout of
    the NIRC2 image (North is up, East is left, scale is set by the
    separation of the binary).  The lines show 5-$\sigma$ contrast
    limits for the `Alopeke filters, and 6-$\sigma$ contrast limits
    for NIRC2.  {\it Left:} Gaia EDR3 renormalized
    unit weight error (RUWE) point estimates for Kepler\,1627A and
    other members of the $\delta$\,Lyr cluster reported by
    \citet{KounkelCovey2019}.  Since other members of the cluster with
    similar brightnesses have comparable degrees of photometric
    variability, the high RUWE suggests that Kepler\,1627 is a
    binary. 
    \label{fig:kep1627binary}
	}
\end{figure*}

@@

% (0.7-2.0\% V-band to G-band dmag difference from EEM table; NOTE
% could determine using model spectra)
Could the companion be creating a false positive signal?  The
companion star contributes $\approx$1\% of the total flux observed in
the Kepler aperture.  The observed transit has a depth of 0.18\%.  An
18\% deep eclipse of the secondary star would therefore be needed to
produce a signal with the appropriate depth.  The shape of the
observed signal requires the impact parameter to be below 0.74
(Table~\ref{tab:posterior}); the body transiting the secondary would
therefore need to be non-grazing with $R_3/R_2 \approx 0.42$.
Assuming a $\approx 0.42R_\odot$ radius of the imaged secondary, this
would imply a tertiary stellar radius of $\approx 0.2R_\odot$.  This
yields a contradiction:  this scenario would require an ingress and
egress phase that each span $\approx$40\% of the transit duration
($\approx 65\,{\rm minutes}$).  The actual measured ingress and egress
duration is $\approx 15\,{\rm minutes}$), 4.4$\times$ shorter.  The
combination of the companion's brightness, transit depth, and ingress
duration therefore rule out the scenario that it could explain the
transit signal.  Two other arguments presented in the main text -- the
inferred stellar density, and the TTV-local slope correlation --
confirm this point.

>>>>

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler and TESS views of the $\delta$\,Lyr cluster.} Colored
    points are kinematically selected candidate $\delta$\,Lyr
    cluster members.  Both Kepler (gray panels) and TESS observed portions of
    the cluster.  Naked-eye stars ($m_{\rm V}<6.5$) are shown in gray or orange.
    Kepler\,1627 (green star) was observed during the entirety of the
    Kepler mission.  Colors of candidate cluster members indicate the
    duration of TESS observations to date, in units of lunar months.
    \label{fig:skychart}
	}
\end{figure}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.7\textwidth]{f15c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is \clusterage\ old.}  {\it Top:}
    Color-absolute magnitude diagram of candidate \cn\ members, in addition to
    stars in IC\,2602 ($\approx38$\,Myr), the Pleiades ($\approx
    115$\,Myr; \citealt{dahm_2015}), and the Gaia EDR3 Catalog of
    Nearby Stars (gray background).  The zoomed right panel
    highlights the pre-main-sequence.  The \cn\ and IC\,2602 are
    approximately the same isochronal age.  {\it Bottom:} TESS and
    Kepler stellar rotation period versus dereddened Gaia color,
    with the Pleiades and Praesepe (650\,Myr) shown for reference
    \citep{rebull_rotation_2016a,douglas_poking_2017}.  Most
    candidate \cn\ members are gyrochronally younger than the
    Pleiades; outliers are probably field interlopers.
   \label{fig:age}
	}
\end{figure*}

@@

		\subfloat{
			\includegraphics[width=\textwidth]{f5.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The full Kepler dataset spans 1{,}437 days (3.9 years), sampled at
    30 minute cadence.  A one hundred day segment is shown here.  The
    top panel shows the \texttt{PDCSAP} median-subtracted flux in
    units of parts-per-thousand ($\times 10^{-3}$).  The dominant
    signal is induced by starspots.  The model for the stellar
    variability (orange line) is subtracted below, revealing the
    transits of \pn, as well as other deviations from the model.  The
    online Figure Set shows the entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627Ab, with stellar variability
    removed.  The 2-$\sigma$ model uncertainties and the maximum {\it
    a posteriori} model are shown as the faint purple band, and the
    dark purple line.  Gray points are individual \texttt{PDCSAP} flux
    measurements; black points are binned to 20 minutes, with a
    representative error bar shown.  The asymmetric residual visible
    during the transit is robust against detrending methods; we
    believe that it is caused by starspot crossings.
    \label{fig:lc}
  }
\end{figure*}

@@

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f16.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
    {\it Top:} 
    The time of each Kepler transit was measured, along with the local
    slope of the light curve.  The two quantities appear
    anti-correlated, which is most easily explained by starspot
    crossings during the first (second) half of transit inducing a
    positive (negative) TTV, provided that the orbit is prograde
    \citep{mazeh_time_2015}.  The units along the abscissa are most
    easily understood by considering that the stellar flux
    changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
    {\it Bottom:} Radial velocities acquired using Keck/HIRES during
    the transit of 2021 Aug 7, observed simultaneously with MuSCAT3
    ({\it griz} photometry).  A quadratic baseline trend was allowed
    in the RV fit.  The best-fit sky-projected obliquity in this model
    is listed in red; the spectroscopic detection however has marginal statistical
    significance compared to a ``trend-only'' model.
    \label{fig:obliquity}
	}
\end{figure}
\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f14.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting
			exoplanets}.  Planets older than $10^9$ years are shown with gray
		markers.  Planets younger than a gigayear with ${\rm
			\tau}/\sigma_{\rm \tau} > 3$ are emphasized, for $\tau$ the age.
		\pn\ is shown with a
		star.  The large sizes of the youngest transiting planets could be
		explained by their primordial atmospheres not yet having
		evaporated; direct measurements of the atmospheric outflows or
		planetary masses would help to confirm this expectation.
		Selection effects may also be important.  Parameters are from the
		NASA Exoplanet Archive (2021 July 2).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

Could the transit signal be produced by anything other than a planet
orbiting this near-solar analog?  \citet{morton_false_2016} validated
the planet based on the transit shape, arguing that the most probable 
false positive scenario was that of a background eclipsing binary,
which had a model-dependent probability of $\approx10^{-5}$.
As we describe in Appendix~\ref{app:companionstar} however,
Kepler\,1627A is accompanied by a low-mass stellar companion ($M_{\rm
B}\approx 0.33\,M_\odot$).  We therefore reconsidered this false
positive scenario in some detail.

% Baraffe+15: M_B 0.33 Mdot
% Rstar = 0.455 --> 0.465 Rsun
%

@@

There are three new lines of evidence that support the planetary
interpretation.  First, the transit duration and the orbital period
are inconsistent with an eclipsing body around the M-dwarf companion:
we find $\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for the companion is
$\approx 4.6\,{\rm g\,cm}^{-3}$ (Table~\ref{tab:posterior};
\citealt{choi_mesa_2016}).  The transit duration is therefore too long
to be explained by a star eclipsing the M dwarf secondary at
$10$-$\sigma$.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f17.pdf}
			\includegraphics[width=0.48\textwidth]{f6.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Kepler 1627 is a binary.} {\it Left:} High-resolution imaging
    from Gemini-North/`Alopeke and Keck/NIRC2 shows an $\approx$M2.5V
    companion at $\rho \approx 0\farcs16$, which corresponds to a
    projected separation of $53\pm4$\,AU.  The inset shows a cutout of
    the NIRC2 image (North is up, East is left, scale is set by the
    separation of the binary).  The lines show 5-$\sigma$ contrast
    limits for the `Alopeke filters, and 6-$\sigma$ contrast limits
    for NIRC2.  {\it Left:} Gaia EDR3 renormalized
    unit weight error (RUWE) point estimates for Kepler\,1627A and
    other members of the $\delta$\,Lyr cluster reported by
    \citet{KounkelCovey2019}.  Since other members of the cluster with
    similar brightnesses have comparable degrees of photometric
    variability, the high RUWE suggests that Kepler\,1627 is a
    binary. 
    \label{fig:kep1627binary}
	}
\end{figure*}

@@

% (0.7-2.0\% V-band to G-band dmag difference from EEM table; NOTE
% could determine using model spectra)
Could the companion be creating a false positive signal?  The
companion star contributes $\approx$1\% of the total flux observed in
the Kepler aperture.  The observed transit has a depth of 0.18\%.  An
18\% deep eclipse of the secondary star would therefore be needed to
produce a signal with the appropriate depth.  The shape of the
observed signal requires the impact parameter to be below 0.74
(Table~\ref{tab:posterior}); the body transiting the secondary would
therefore need to be non-grazing with $R_3/R_2 \approx 0.42$.
Assuming a $\approx 0.46R_\odot$ radius of the imaged secondary
from the \citet{baraffe_new_2015} models, this
would imply a tertiary stellar radius of $\approx 0.2R_\odot$.  This
yields a contradiction:  this scenario would require an ingress and
egress phase that each span $\approx$40\% of the transit duration
($\approx 65\,{\rm minutes}$).  The actual measured ingress and egress
duration is $\approx 15\,{\rm minutes}$), 4.4$\times$ shorter.  The
combination of the companion's brightness, transit depth, and ingress
duration therefore rule out the scenario that it could explain the
transit signal.  Two other arguments presented in the main text -- the
inferred stellar density, and the TTV-local slope correlation --
confirm this point.
